---
title: "Political Microtargeting"
subtitle: "Safeguarding Democratic Values In Digital Political Practices"
date: ""
output:
  rmdformats::html_docco:
    highlight: kate
---
```{r setup, include=FALSE}
## Global options
knitr::opts_chunk$set(cache = TRUE)
```

<!-- <details open> -->
<!-- <summary><b><font size="+2">Description</font></b></summary> -->

# Description


The Political Microtargeting Project is an interdisciplinary research effort focused on exploring the impact of political microtargeting on democratic processes and legitimacy. 

Led by an experienced team of researchers from the Amsterdam School of Communication Research (ASCoR), and the Institute for Information Law (IViR), the project aims to make microtargeting practices visible, study their impact on citizens and society, and develop policy guidelines to limit their threats and embrace their opportunities. 

The project involves close collaboration with government agencies, non-academic partners, and other stakeholders to ensure that the research findings have a meaningful impact on society.
<!-- </details> -->

# Papers: 

[Votta, F., Noroozian, A., Dobber, T., Helberger, N., & de Vreese, C. (2023). **Going Micro to Go Negative? Targeting Toxicity using Facebook and Instagram Ads.** *Computational Communication Research*, 5(1), 1-50.](https://www.aup-online.com/content/journals/10.5117/CCR2023.1.001.VOTT)

# Media Appearances / References

A list of media appearances and references in TV, radio and newspapers.

+ [Research featured: ZDF Magazin Royale show about microtargeting during Germany 2021 election (in collab with Who Targets Me)](https://www.youtube.com/watch?v=8vq6MzGNZyM)

# Dashboards

Here is a list of dashboards that were created to monitor microtargeting and digital campaigns during election time.

+ `r emo::ji("netherlands")` [2021 Dutch general election](https://favstats.github.io/DutchElectionObservatory/nl/index.html) (15th-17th March 2021)
+ `r emo::ji("germany")` [2021 German general election](https://favstats.shinyapps.io/btw21_wtm/) (26th September 2021)
+ 🇸🇪 [2022 Swedish general election](https://favstats.github.io/SwedishParliamentElection2023/) (11th September 2022)
+ `r emo::ji("us")` [2022 United States midterm elections](https://whotargetsme.shinyapps.io/midterms2022/) (8th November 2022)
+ `r emo::ji("us")` [2022 United States midterm elections - Georgia Runoff](https://whotargetsme.github.io/midterms2022_dashboard/) (6th December 2022)
+ 🇮🇹 [2023 Lazio & Lombardy regional election](https://favstats.github.io/regionali2023/) (12-13th February 2023)
+ 🇪🇪 [2023 Estonian parliamentary election](https://favstats.github.io/EstoniaElection2023/) (5th March 2023)
+ `r emo::ji("netherlands")` [2023 Dutch provincial elections](https://favstats.github.io/ProvincialeStatenverkiezingen2023/) (15th March 2023)
+ 🇲🇪 [2023 Montenegrin presidential elections](https://favstats.github.io/MontenegroPresidentialElection2023/) (19th March 2023)
+ 🇦🇺 [2023 New South Wales state election](https://favstats.github.io/NSWAustralianElection2023/) (25th March 2023)

# Team


```{r, echo=F}
library(htmltools)
library(bs4cards)


cards <- function(title, text, link, image) {
  div(class = "card",
      img(class = "card-img-top", src = image, style="object-fit: cover; height: 200px; width: 100%;"),
      div(class = "card-body",
          h6(class = "card-title", title),
          p(class = "card-text", text),
          a(href = link, class = "btn btn-primary", "Learn more")))
}

div(class = "row",
    div(class = "col-sm-6 col-md-4",
        cards(
          "Prof. dr. N. Helberger",
          "This is a longer card with supporting text below as a natural lead-in to additional content. This content is a little bit longer.",
          "#",
          "https://verfassungsblog.de/wp-content/uploads/2022/08/Natali-Helberger-Global-Digital-Cultures-UvA.jpg"
        )
    ),
    div(class = "col-sm-6 col-md-4",
        cards(
          "Prof. dr. C. de Vreese",
          "This is a longer card with supporting text below as a natural lead-in to additional content. This content is a little bit longer.",
          "#",
          "https://www.uva.nl/binaries/_ht_1677599571673/cardmedium/content/gallery/personen/v/o/fabio-votta.jpg"
        )
    ),
    div(class = "col-sm-6 col-md-4",
        cards(
          "Prof. dr. B. Roessler",
          "This is a longer card with supporting text below as a natural lead-in to additional content. This content is a little bit longer.",
          "#",
          "https://www.uva.nl/binaries/content/documents/personalpages/d/r/m.z.vandrunen/m.z.van-drunen/m.z.van-drunen/uva%3Aprofileimagecompound"
        )
    )
)

```

```{r, echo = F}

div(class = "row",
    div(class = "col-sm-6 col-md-4",
        cards(
          "Prof. dr. N. Helberger",
          "This is a longer card with supporting text below as a natural lead-in to additional content. This content is a little bit longer.",
          "#",
          "https://verfassungsblog.de/wp-content/uploads/2022/08/Natali-Helberger-Global-Digital-Cultures-UvA.jpg"
        )
    ),
    div(class = "col-sm-6 col-md-4",
        cards(
          "PhD candidate F. Votta",
          "This is a longer card with supporting text below as a natural lead-in to additional content. This content is a little bit longer.",
          "#",
          "https://www.uva.nl/binaries/_ht_1677599571673/cardmedium/content/gallery/personen/v/o/fabio-votta.jpg"
        )
    ),
    div(class = "col-sm-6 col-md-4",
        cards(
          "Postdoc M. van Drunen",
          "This is a longer card with supporting text below as a natural lead-in to additional content. This content is a little bit longer.",
          "#",
          "https://www.uva.nl/binaries/content/documents/personalpages/d/r/m.z.vandrunen/m.z.van-drunen/m.z.van-drunen/uva%3Aprofileimagecompound"
        )
    )
)

```


# Further Reading

[Towards unfair political practices law: Learning lessons from the regulation of unfair commercial practices for online political advertising.](https://www.jipitec.eu/issues/jipitec-12-3-2021/5338)



<script>
.ui.card {
  margin-bottom: 1em;
}

.ui.card .image img {
  height: 75px;
  width: 75px;
  object-fit: cover;
  border-radius: 50%;
}

.ui.card .content {
  text-align: center;
}

.ui.card .header {
  margin-top: 1em;
  font-size: 1.2em;
}

.ui.card .description {
  margin-top: 1em;
  font-size: 1em;
}


</script>

